---
title: "visualiseScholar_workSheet"
author: "Bastien Boutonnet"
date: "15 January 2016"
output: html_document
---

## Libraries
```{r}
library(scholar)
library(ggplot2)
library(grid)
library(gridExtra)
```

## Example Data
```{r}
prof=get_profile('FYrnmlIAAAAJ')
his=get_citation_history('FYrnmlIAAAAJ')
his$year=as.factor(his$year)
```

## Plot styles repo
### Blue 'gradiant' bar plot
```{r}
histGraph=ggplot(data=history, aes(x=year, y=cites,fill=cites)) #fill will colour the bars.
histGraph+geom_bar(stat='identity',width=.7)+
    scale_fill_gradient(low = "lightskyblue", high = "steelblue")+ #colours the bars should take
    theme(panel.background=element_blank())+ #removes grey background
    theme(panel.grid=element_blank())+ #removes lines for the grid
    theme(axis.ticks=element_blank())+ #removes ticks on both axes
    theme(axis.text.y=element_blank())+ #removes tick text for y axis
    theme(axis.title=element_blank())+ #removes axes titles
    scale_y_discrete(expand = c(0, 0))+ #makes sure y starts at 0
    theme(legend.position='none') #removes the legend
```

### Line & Dot plot
```{r}
histGraph=ggplot(data=history, aes(x=year, y=cites))
histGraph+geom_line(stat='identity',aes(group=1),colour='black')+
    geom_point(size=3,colour='black',fill='lightskyblue',pch=21)+
    theme(panel.background=element_blank())+ #removes grey background
    theme(panel.grid=element_blank())+ #removes lines for the grid
    theme(axis.ticks=element_blank())+ #removes ticks on both axes
    theme(axis.text.y=element_blank())+ #removes tick text for y axis
    theme(axis.title=element_blank())+ #removes axes titles
    theme(legend.position='none') #removes the legend
```

### *À la* Github
Figure out how to do a tile plot
```{r}
```

## Todo:
- have a basic `prepDat()` function:
  - it will pull out the data, mainly using `scholar()` and prepare it into variables to be used after.
- make a `genPlot()` function:
  - this one will just make an appropriate `ggplot()` call to map layers on data
- make a `pimpPlot()` function:
  - this one will choose and append to the `genPlot()` output the correct styling options in store.
  - it will also be the function that outputs the plot viz.
  - it could also have an option to call for a `customStyle` object which the user will have previously loaded.
- make a `showBoringPlot()` function:
  - this one outputs a ggplot element with the "boring" plot to be custom styled.

## Function Repo:
```{r}
prepDat <- function(id) {
  prof=get_profile(id)
  his=get_citation_history(id)
  his$year=as.factor(his$year)
  
  return(list(prof=prof,his=his))
}

genPlot <- function(id,his) {
  dat <- prepDat(id)
  hist=dat$his
  histGraph=ggplot(data=hist, aes(x=year, y=cites))
  return(histGraph)
}

pimpPlot <- function(histGraph,whichStyle='lines',custStyle=NULL) {
  if (whichStyle=='lines') {
    
  }
  if (whichStyle=='bars') {
    
  }
  if (whichStyle=='git'){
    
  }
  if (whichStyle=='custom') {
    #here look up the `custStyle` var
  }
}
```